Computational Methods for Principle Component Analysis Applied to Genotype Data

### 2018-02-24 doc/paper.tex
Add readme
Add nChg and mChg plots to paper.

See plots.

@@

\includegraphics[width=0.98\textwidth]{runtimes_rand}

\includegraphics[width=0.98\textwidth]{err_refcenter_rand}

\includegraphics[width=0.98\textwidth]{err_trace_rand}

\includegraphics[width=0.98\textwidth]{err_refcenter_rand}

\includegraphics[width=0.98\textwidth]{kgn_allChr_ukb_orphans_ukb_1k_comb}

@@

\includegraphics[width=0.98\textwidth]{kgn_allChr_ukb_orphans_ukb_1k_rand}

>>>>

See \Cref{fig:nChg} and \Cref{fig:mChg} for the comparison of the runtimes and accuracy.

@@

\begin{figure}[p]
  \label{fig:nChg}
  \centering
  \includegraphics[width=0.98\textwidth]{nChg}
  \caption{
    Runtimes and deviations for different methods as the reference sample size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
\end{figure}

\begin{figure}[p]
  \label{fig:mChg}
  \centering
  \includegraphics[width=0.98\textwidth]{mChg}
  \caption{
    Runtimes and deviations for different methods as the study sample size increases.
    The reference sample size is fixed to 600 and the number of SNPs is 100,000 (1000 per genealogy).
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
\end{figure}

% \includegraphics[width=0.98\textwidth]{runtimes_rand}

% \includegraphics[width=0.98\textwidth]{err_refcenter_rand}

% \includegraphics[width=0.98\textwidth]{err_trace_rand}

% \includegraphics[width=0.98\textwidth]{err_refcenter_rand}

% \includegraphics[width=0.98\textwidth]{kgn_allChr_ukb_orphans_ukb_1k_comb}

@@

% \includegraphics[width=0.98\textwidth]{kgn_allChr_ukb_orphans_ukb_1k_rand}
